Untitled

### 2022-06-06 Manuscript/Lanuza_et_al_2021.Rmd
edits

[Esta última parte intenta justificar la validación de nuestros resultados, le vendría bien ojo crítico, antes estaba en el siguiente párrafo pero la maldad mental para criticarnos se genera en este y pienso que ya no llega al siguiente con buenos ojos](Jose)

@@

We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species. For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera. Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space. In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of records counted (7.55% of the total). This finding is consistent with previous research showing that *A. mellifera* was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018]. Hence, to control for the effect of *A. mellifera* on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A. mellifera*. We found that *A. mellifera*, was partly driving some of the observed trends on PC1 (Fig. S4). However, we did not detect major differences on PC2 and PC3.

@@

[Aqui hay que convencer que usar el dataset de floral rewards es lo mas adecuado]()

Second, to better understand complex trait relationships, we used regression trees. Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction. We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2). We conducted this analysis using the *rpart* function from the *rtrees* package [@therneau2015] with method *'anova'* with a minimum of 50 observations per terminal node and we used the *rpart.plot* package [@milborrow2015] to plot the regression trees. We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors. We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits. We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig. S5).

@@

The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (Fig. 1 and Fig. S6). The first principal component (PC1) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size ('flower number - flower size'). The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33). One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number. For instance, on this end of the spectrum we find the species *Cornus florida* which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower. The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers. For instance, on this side of the axis we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower. The second principal component (PC2) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively. The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3). In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles. A species example of this side of the spectrum is *Zuccagnia punctata* that is a self incompatible shrub which depends totally on floral visitors, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm. In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles. For instance, on this side of the spectrum we find the species *Veronica peregrina* which is a self compatible herb that is thought to be almost a complete selfer, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm. Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51). The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3). In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig. S7). This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).

>>>>

@@

We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species. For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera. Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space. In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of records counted (7.55% of the total). This finding is consistent with previous research showing that *A. mellifera* was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018]. Hence, to control for the effect of *A. mellifera* on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A. mellifera*. We found that *A. mellifera*, was partly driving some of the observed trends on PC1 (Fig. S5). However, we did not detect major differences on PC2 and PC3.

@@

Second, to better understand complex trait relationships, we used regression trees. Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction. We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2). We conducted this analysis using the *rpart* function from the *rtrees* package [@therneau2015] with method *'anova'* with a minimum of 50 observations per terminal node and we used the *rpart.plot* package [@milborrow2015] to plot the regression trees. We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors. We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits. Because pollen and nectar traits are essential to understand plant-pollinator interactions [@heinrich1972; @johnson2008; @vaudo2015], we focused in the main text on the regression trees that included floral rewards. Indeed, we found that nectar and pollen traits were among the best traits for explaining the different species-level metrics (Fig. S6).

@@

The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (Fig. 1 and Fig. S7). The first principal component (PC1) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size ('flower number - flower size'). The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33). One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number. For instance, on this end of the spectrum we find the species *Cornus florida* which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower. The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers. For instance, on this side of the axis we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower. The second principal component (PC2) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively. The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3). In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles. A species example of this side of the spectrum is *Zuccagnia punctata* that is a self incompatible shrub which depends totally on floral visitors, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm. In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles. For instance, on this side of the spectrum we find the species *Veronica peregrina* which is a self compatible herb that is thought to be almost a complete selfer, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm. Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51). The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3). In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig. S4). This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).

### 2022-06-06 Manuscript/Lanuza_et_al_2021.tex
edits

\href{Jose}{Esta última parte intenta justificar la validación de nuestros resultados, le vendría bien ojo crítico, antes estaba en el siguiente párrafo pero la maldad mental para criticarnos se genera en este y pienso que ya no llega al siguiente con buenos ojos}

@@

We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species. For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera. Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space. In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total). This finding is consistent with previous research showing that \emph{A. mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung et al., 2018}). Hence, to control for the effect of \emph{A. mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding \emph{A. mellifera}. We found that \emph{A. mellifera}, was partly driving some of the observed trends on PC1 (Fig. S4). However, we did not detect major differences on PC2 and PC3.

@@

Second, to better understand complex trait relationships, we used regression trees. Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction. We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2). We conducted this analysis using the \emph{rpart} function from the \emph{rtrees} package (\protect\hyperlink{ref-therneau2015}{Therneau et al., 2015}) with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow, 2015}) to plot the regression trees. We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors. We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits. We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig. S5).

@@

The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (Fig. 1 and Fig. S6). The first principal component (PC1) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size (`flower number - flower size'). The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33). One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number. For instance, on this end of the spectrum we find the species \emph{Cornus florida} which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower. The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers. For instance, on this side of the axis we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower. The second principal component (PC2) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively. The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3). In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles. A species example of this side of the spectrum is \emph{Zuccagnia punctata} that is a self incompatible shrub which depends totally on floral visitors, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm. In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles. For instance, on this side of the spectrum we find the species \emph{Veronica peregrina} which is a self compatible herb that is thought to be almost a complete selfer, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm. Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51). The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3). In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig. S7). This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).

@@

@@

@@

>>>>

@@

We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species. For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera. Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space. In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total). This finding is consistent with previous research showing that \emph{A. mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung et al., 2018}). Hence, to control for the effect of \emph{A. mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding \emph{A. mellifera}. We found that \emph{A. mellifera}, was partly driving some of the observed trends on PC1 (Fig. S5). However, we did not detect major differences on PC2 and PC3.

@@

Second, to better understand complex trait relationships, we used regression trees. Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction. We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2). We conducted this analysis using the \emph{rpart} function from the \emph{rtrees} package (\protect\hyperlink{ref-therneau2015}{Therneau et al., 2015}) with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow, 2015}) to plot the regression trees. We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors. We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits. Because pollen and nectar traits are essential to understand plant-pollinator interactions (\protect\hyperlink{ref-heinrich1972}{Heinrich \& Raven, 1972}; \protect\hyperlink{ref-johnson2008}{Johnson \& Nicolson, 2008}; \protect\hyperlink{ref-vaudo2015}{Vaudo et al., 2015}), we focused in the main text on the regression trees that included floral rewards. Indeed, we found that nectar and pollen traits were among the best traits for explaining the different species-level metrics (Fig. S6).

@@

The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (Fig. 1 and Fig. S7). The first principal component (PC1) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size (`flower number - flower size'). The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33). One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number. For instance, on this end of the spectrum we find the species \emph{Cornus florida} which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower. The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers. For instance, on this side of the axis we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower. The second principal component (PC2) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively. The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3). In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles. A species example of this side of the spectrum is \emph{Zuccagnia punctata} that is a self incompatible shrub which depends totally on floral visitors, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm. In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles. For instance, on this side of the spectrum we find the species \emph{Veronica peregrina} which is a self compatible herb that is thought to be almost a complete selfer, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm. Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51). The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3). In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig. S4). This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).

@@

\leavevmode\vadjust pre{\hypertarget{ref-heinrich1972}{}}%
Heinrich, B., \& Raven, P. H. (1972). Energetics and pollination ecology: The energetics of pollinators may have wide implications in floral biology and community ecology. \emph{Science}, \emph{176}(4035), 597--602.

@@

\leavevmode\vadjust pre{\hypertarget{ref-johnson2008}{}}%
Johnson, S. D., \& Nicolson, S. W. (2008). Evolutionary associations between nectar properties and specificity in bird pollination systems. \emph{Biology Letters}, \emph{4}(1), 49--52.

@@

\leavevmode\vadjust pre{\hypertarget{ref-vaudo2015}{}}%
Vaudo, A. D., Tooker, J. F., Grozinger, C. M., \& Patch, H. M. (2015). Bee nutrition and floral resource restoration. \emph{Current Opinion in Insect Science}, \emph{10}, 133--141.

### 2022-06-06 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edits

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.cap="\\textbf{Fig. S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level. Note that for visualization purposes studies from the same authors are shown with the same colour."}

@@

set.seed(12)
ggplot(data = world) +
  geom_sf(fill="antiquewhite", color="grey49") +
  xlab("Longitude") + ylab("Latitude") +
  geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
           size = 3.5, stroke=1)+ 
  theme(panel.grid.major = element_line(color = gray(.5), 
linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
  scale_x_continuous(breaks = c(-100,0, 100)) +
  theme(legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=6),
         legend.title = element_text(size=12)) +   scale_colour_manual(values = colors) + labs(colour="Plant-pollinator studies")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="80%",fig.align='center',fig.cap= "\\textbf{Fig. S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation. Panel A shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel B shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=10,out.width="80%",fig.align='center',fig.cap="\\textbf{Fig. S4.} Comparison of the phylogenetic informed principal component analysis for the subset of species that had information of floral rewards with data imputation and without data imputation. Panel A shows the reproductive spectrum of trait variation for the dataset with data imputation and panel B shows the reproductive spectrum for the dataset excluding species with missing trait data"}
setwd("~/R_Projects/Reproductive Traits")

>>>>

\newpage
\blandscape

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.width=12, fig.height=6, fig.cap="\\textbf{Fig. S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level. Note that for visualization purposes studies from the same authors are shown with the same colour."}

@@

set.seed(12)
ggplot(data = world) +
  geom_sf(fill="antiquewhite", color="grey49") +
  xlab("Longitude") + ylab("Latitude") +
  geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
           size = 4.5, stroke=1)+ 
  theme(panel.grid.major = element_line(color = gray(.5), 
linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
  scale_x_continuous(breaks = c(-100,0, 100)) +
  theme(legend.key.size = unit(0.6, 'cm'), legend.text = element_text(size=10),
         legend.title = element_text(size=12)) +   scale_colour_manual(values = colors) + labs(colour="Plant-pollinator studies")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="60%",fig.align='center',fig.cap= "\\textbf{Fig. S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation. Panel A shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel B shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=10,out.width="60%",fig.align='center',fig.cap="\\textbf{Fig. S4.} Comparison of the phylogenetic informed principal component analysis for the subset of species that had information of floral rewards with data imputation and without data imputation. Panel A shows the reproductive spectrum of trait variation for the dataset with data imputation and panel B shows the reproductive spectrum for the dataset excluding species with missing trait data"}
setwd("~/R_Projects/Reproductive Traits")

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(cowplot)
# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.75)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(1.2, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}
